---
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: yeti
    css: "ReportDashboardStyles.css"
editor_options: 
  chunk_output_type: console
---

Trip Generation {data-navmenu="Long-Distance Model"}
============================================

Highlights Column {data-width=150}
--------------------------------------------

**Long-Distance Model: Trip Generation**

Long-distance model trip summaries.

### Total Daily Trips

```{r Daily_Trips_ValueBox}
value <- format(ld_trips[, sum(Trips)], big.mark = ",",  digits = 3, nsmall = 0, scientific = FALSE, trim = TRUE)
valueBox(value, caption = "Total Daily Trips", icon = "fa-cube")
```

### External-to-Internal (XI) Daily Trips

```{r Daily_XI_Trips_ValueBox}
value <- format(ld_trips[Movement.Type == "XI", sum(Trips)], big.mark = ",",  digits = 3, nsmall = 0, scientific = FALSE, trim = TRUE)
valueBox(value, caption = "External-to-Internal (XI) Daily Trips", icon = "fa-arrow-down")
```

### Internal-to-External (IX) Daily Trips

```{r Daily_IX_Trips_ValueBox}
value <- format(ld_trips[Movement.Type == "IX", sum(Trips)], big.mark = ",", digits = 3, nsmall = 0, scientific = FALSE, trim = TRUE)
valueBox(value, caption = "Internal-to-External (IX) Daily Trips", icon = "fa-arrow-up")
```

### External-to-External (XX) Daily Trips

```{r Daily_XX_Trips_ValueBox}
value <- format(ld_trips[Movement.Type == "XX", sum(Trips)], big.mark = ",", digits = 3, nsmall = 0, scientific = FALSE, trim = TRUE)
valueBox(value, caption = "External-to-External (XX) Daily Trips", icon = "fa-arrows")
```

Column {data-width=400, .tabset}
--------------------------------------------
### Long-Distance Trips by Movement Type

```{r Map_Long_Distance_Trips}
k <- 10

dat <- rbind(ld_trips[Movement.Type %in% c("IX"), .(Trips = sum(Trips)), keyby = .(TAZ = OTAZ, Movement.Type)],
             ld_trips[Movement.Type %in% c("XI"), .(Trips = sum(Trips)), keyby = .(TAZ = DTAZ, Movement.Type)])

map <- leaflet() %>%
  addProviderTiles(map_type, group = "Background Map")
map <- map %>% addTAZPoints(data = dat,
                            shp = shp, group = "Movement.Type",
                            scale.factor = k, TAZcol = "TAZ", 
                            weight = "Trips") %>%
  addPolygons(data = shp, weight = 0.5,
              opacity = 0.25, color = "grey",
              fillOpacity = 0, fillColor = "white") %>%
  addTAZPolygons()
map %>% htmlwidgets::onRender(JS(paste0("function(el, x){
var map = this;
var corner1 = new L.LatLng(",SEMCOG_BBOX["ymin"],", ",SEMCOG_BBOX["xmin"],"),
    corner2 = new L.LatLng(",SEMCOG_BBOX["ymax"],", ",SEMCOG_BBOX["xmax"],"),
    bounds = new L.LatLngBounds(corner1, corner2);
map.fitBounds(bounds);
}")))
```

>`r if(SCENARIO_RUN_LDM) {paste0("Note: Each data point represents ", comma(k), " long-distane trips and precise locations are illustrative as trip origins and destinations are only identified geographically at the TAZ-level.")}`


Column {data-width=400, .tabset}
--------------------------------------------

### IX/XI Trips by County

```{r Chart_Long-Distance_Trips_by_Region}
# Organize
dat <- rbind(ld_trips[Movement.Type %in% c("IX"), .(Trips = sum(Trips)), keyby = .(Region = Region.Origin, Movement.Type)],
             ld_trips[Movement.Type %in% c("XI"), .(Trips = sum(Trips)), keyby = .(Region = Region.Destination, Movement.Type)])

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Long-Distance_Trips_by_County.csv"), row.names = FALSE)
assign("db_tab_ld_trips_county", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Region", yvar = "Trips", xlabel = "County", ylabel = "Long-Distance Trips", fill = "Movement.Type", coord_flip = TRUE)
```

### Trips by External Station 

```{r Chart_Long-Distance_Trips_by_External}
# Organize
dat <- rbind(ld_trips[Movement.Type %in% c("IX", "XX") & DTAZ %in% BASE_TAZ_EXTERNAL, .(Trips = sum(Trips)), keyby = .(External = DStationName, ExternalGroup = DStationGroup, Movement.Type)],
             ld_trips[Movement.Type %in% c("XI", "XX") & OTAZ %in% BASE_TAZ_EXTERNAL, .(Trips = sum(Trips)), keyby = .(External = OStationName, ExternalGroup = OStationGroup, Movement.Type)])
dat[, ExternalName := paste0(External, " (", ExternalGroup, ")")]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Long-Distance_Trips_by_External.csv"), row.names = FALSE)
assign("db_tab_ld_trips_external", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "ExternalName", yvar = "Trips", xlabel = "External Station", ylabel = "Long-Distance Trips", fill = "Movement.Type", position = "dodge", coord_flip = TRUE)
```

> External to internal trips and internal to external trips pass through one external station, on their way into the region and on the way out of the region respectively. External to external trips pass through two external stations, both on their way into and on the way out of the region. 

### Trips by Time Period 

```{r Chart_Long-Distance_Trips_by_TOD}
# Organize
dat <- ld_trips[, .(Trips = sum(Trips)), keyby = .(Movement.Type, TOD)]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Long-Distance_Trips_by_TOD.csv"), row.names = FALSE)
assign("db_tab_ld_trips_tod", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "TOD", yvar = "Trips", xlabel = "Time Period", ylabel = "Long-Distance Trips", fill = "Movement.Type", position = "dodge")
```

### Trips by External Station (Table)

```{r Table_Long-Distance_Trips_by_External}
# Organize
dat <- rbind(ld_trips[Movement.Type %in% c("IX", "XX") & DTAZ %in% BASE_TAZ_EXTERNAL, .(Trips = round(sum(Trips)), Direction = "Outbound"), keyby = .(TAZ = DTAZ, External = DStationName, ExternalGroup = DStationGroup, Movement.Type)],
             ld_trips[Movement.Type %in% c("XI", "XX") & OTAZ %in% BASE_TAZ_EXTERNAL, .(Trips = round(sum(Trips)), Direction = "Inbound"), keyby = .(TAZ = OTAZ, External = OStationName, ExternalGroup = OStationGroup, Movement.Type)])

dat <- add_totals(dcast.data.table(dat,
                                   TAZ + External + ExternalGroup ~ Movement.Type + Direction,
                                   fun.aggregate = sum,
                                   value.var = "Trips"),
                  idcols = 3L)

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Long-Distance_Trips_by_External_TAZ.csv"), row.names = FALSE)
assign("db_tab_ld_trips_external_taz", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")

```

### Trips by Time Period (Table)

```{r Table_Long-Distance_Trips_by_External_TOD}
# Organize
dat <- rbind(ld_trips[Movement.Type %in% c("IX", "XX") & DTAZ %in% BASE_TAZ_EXTERNAL, .(Trips = round(sum(Trips)), Direction = "Outbound"), keyby = .(External = DStationName, ExternalGroup = DStationGroup, Movement.Type, TOD)],
             ld_trips[Movement.Type %in% c("XI", "XX") & OTAZ %in% BASE_TAZ_EXTERNAL, .(Trips = round(sum(Trips)), Direction = "Inbound"), keyby = .(External = OStationName, ExternalGroup = OStationGroup, Movement.Type, TOD)])

fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Long-Distance_Trips_by_External_TOD_ODSeg.csv"), row.names = FALSE)

dat <- add_totals(dcast.data.table(dat,
                                   External + ExternalGroup ~ TOD,
                                   fun.aggregate = sum,
                                   value.var = "Trips"),
                  idcols = 2L)

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Long-Distance_Trips_by_External_TOD.csv"), row.names = FALSE)
assign("db_tab_ld_trips_external_tod", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")

```


Trip Distribution {data-navmenu="Long-Distance Model"}
============================================

**Long-Distance Model: Trip Distribution**

Long-distance model trip results by OD segment and distance.

Highlights Column {data-width=150}
--------------------------------------------

### Total Vehicle Miles Traveled

```{r Daily_LD_VMT_ValueBox}
value <- format(ld_trips[, sum(Trips * Distance)], big.mark = ",",  digits = 3, nsmall = 0, scientific = FALSE, trim = TRUE)
valueBox(value, caption = "Total Daily VMT", icon = "fa-cube")
```

### IX/XI Vehicle Miles Traveled

```{r Daily_IXXI_VMT_ValueBox}
value <- format(ld_trips[Movement.Type %in% c("IX", "XI"), sum(Trips * Distance)], digits = 3, nsmall = 0, big.mark = ",",  scientific = FALSE, trim = TRUE)
valueBox(value, caption = "IX/XI Daily VMT", icon = "fa-arrows")
```

### XX Vehicle Miles Traveled

```{r Daily_XX_VMT_ValueBox}
value <- format(ld_trips[Movement.Type == "XX", sum(Trips * Distance)], big.mark = ",",  digits = 3, nsmall = 0, scientific = FALSE, trim = TRUE)
valueBox(value, caption = "XX Daily VMT", icon = "fa-arrows")
```

### Average Trip Distance

```{r Daily_LD_AveDist_ValueBox}
value <- format(ld_trips[, sum(Trips * Distance)/sum(Trips)], big.mark = ",",  digits = 3, nsmall = 1, scientific = FALSE, trim = TRUE)
valueBox(value, caption = "Average Trip Distance", icon = "fa-cube")
```

### Average IX/XI Trip Distance

```{r Daily_IXXI_AveDist_ValueBox}
value <- format(ld_trips[Movement.Type %in% c("IX", "XI"), sum(Trips * Distance)/sum(Trips)], big.mark = ",", digits = 3, nsmall = 1, scientific = FALSE, trim = TRUE)
valueBox(value, caption = "IX/XI Average Trip Distance", icon = "fa-arrows")
```

### Average XX Trip Distance

```{r Daily_XX_AveDist_ValueBox}
value <- format(ld_trips[Movement.Type == "XX", sum(Trips * Distance)/sum(Trips)], big.mark = ",", digits = 3, nsmall = 1, scientific = FALSE, trim = TRUE)
valueBox(value, caption = "XX Average Trip Distance", icon = "fa-arrows")
```


Column {data-width=300, .tabset}
--------------------------------------------

### Trip Length

```{r Chart_Long-Distance_Trip_Length}
# Organize
dist_bin <- seq(0, 150, by = 10)
dat <- ld_trips[Trips > 0, .(Distance, Trips, Movement.Type)]
dat[, DistBin := dist_bin[findInterval(Distance, dist_bin)]]
dat <- dat[,.(Trips = sum(Trips)), keyby = .(DistBin, Movement.Type)]
dat[, PctTrips := Trips/sum(Trips), by = Movement.Type]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Long-Distance_Trips_by_DistBin.csv"), row.names = FALSE)
assign("db_tab_ld_trips_distbin", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "DistBin", yvar = "PctTrips", xlabel = "Distance (Lower Bound)", ylabel = "Percent of Long-Distance Trips", fill = "Movement.Type", position = "dodge")

```

> Trip length frequency in 10 mile bins (e.g, 0-10 miles, 10-20 miles) with lower bound of distance bin labelled. Distances are SEMCOG network distances only, i.e., from external station to internal TAZ or vice versa for XI and IX trips, and from external station to external station for XX trips.

### IX/XI Origin-Destination Summary

```{r Chart_Long-Distance_IXXI_OD_Summary}
# Organize
dat <- rbind(ld_trips[Movement.Type %in% c("IX"), .(Trips = sum(Trips)), keyby = .(Region = Region.Origin, ExternalGroup = DStationGroup, Movement.Type)],
             ld_trips[Movement.Type %in% c("XI"), .(Trips = sum(Trips)), keyby = .(Region = Region.Destination, ExternalGroup = OStationGroup, Movement.Type)])

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Long-Distance_Trips_IXXIODSummary.csv"), row.names = FALSE)
assign("db_tab_ld_trips_ixxi_od", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Region", yvar = "Trips", xlabel = "County", ylabel = "Long-Distance Trips", fill = "ExternalGroup", position = "stack", xrotate = TRUE)

```

### XX Origin-Destination Summary

```{r Chart_Long-Distance_XX_OD_Summary}
# Organize
dat <- ld_trips[Movement.Type %in% c("XX"), .(Trips = sum(Trips)), keyby = .(OStationGroup, DStationGroup)]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Long-Distance_Trips_XX_ODSummary.csv"), row.names = FALSE)
assign("db_tab_ld_trips_xx_od", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "OStationGroup", yvar = "Trips", xlabel = "Origin External Station Group", ylabel = "Long-Distance Trips", fill = "DStationGroup", position = "stack")

```


Column {data-width=500, .tabset}
--------------------------------------------

### IX Trips County to External OD

```{r Table_Long-Distance_Trips_IX_OD}
# Organize
dat <- ld_trips[Movement.Type %in% c("IX") & DTAZ %in% BASE_TAZ_EXTERNAL & Trips > 0, 
                      .(Trips = round(sum(Trips))), keyby = .(County = Region.Origin, External = DStationName, ExternalGroup = DStationGroup, Movement.Type)]
dat[, ExternalName := paste0(External, " (", ExternalGroup, ")")]

dat <- add_totals(dcast.data.table(dat,
                                  County ~ ExternalName,
                                   fun.aggregate = sum,
                                   value.var = "Trips"))

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Long-Distance_Trips_IX_County_External.csv"), row.names = FALSE)
assign("db_tab_ld_trips_ix_county_external", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")

```

### XI Trips External to County OD

```{r Table_Long-Distance_Trips_XI_OD}
# Organize
dat <- ld_trips[Movement.Type %in% c("XI") & OTAZ %in% BASE_TAZ_EXTERNAL & Trips > 0, 
                      .(Trips = round(sum(Trips))), keyby = .(County = Region.Destination, External = OStationName, ExternalGroup = OStationGroup)]

dat[, ExternalName := paste0(External, " (", ExternalGroup, ")")]

dat <- add_totals(dcast.data.table(dat,
                                  ExternalName ~ County,
                                   fun.aggregate = sum,
                                   value.var = "Trips"))

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Long-Distance_Trips_XI_External_County.csv"), row.names = FALSE)
assign("db_tab_ld_trips_xi_external_county", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")
```

### XX Trips External to External OD

```{r Table_Long-Distance_Trips_XX_OD}
# Organize
dat <- ld_trips[Movement.Type %in% c("XX") & Trips > 0, 
                      .(Trips = round(sum(Trips))), keyby = .(OStationName, OStationGroup, DStationName, DStationGroup)]
dat[, OExternalName := paste0(OStationName, " (", OStationGroup, ")")]
dat[, DExternalName := paste0(DStationName, " (", DStationGroup, ")")]

dat <- add_totals(dcast.data.table(dat,
                                  OExternalName ~ DExternalName,
                                   fun.aggregate = sum,
                                   value.var = "Trips"))

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "Long-Distance_Trips_XX_External_External.csv"), row.names = FALSE)
assign("db_tab_ld_trips_xx_external_external", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")

```
